Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-08 paper.tex
included held out baseline data for text - the neural network helps!

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
If we gave our agent the full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates,
as well as 2 or 4 input multiplexers.
\system observes the input/output truth table of the circuits.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{multiplexer}, top).

@@

  \\\midrule\multicolumn{6}{c}{\emph{String Editing}}\\\midrule
  \% solved&99\% \\
  Solve time&  0.9s
  \\\bottomrule
  \end{tabular}
\caption{\% solved: fraction solved with 5 sec timeout. Solve time: averaged over solved tasks. MDL: $-\expect\left[\probability[x|p] \right]$. For domains other than symbolic regression MDL is 0 nats. For symbolic regression MDL is a proxy for \# of continuous degrees of freedom.}\label{baselineComparisons}  \end{table}
\pagebreak
 \section{Related Work}
 Our work is far from the first to learn to learn programs,
 an  idea that goes back to Solomonoff~\cite{solomonoff1989system}:

>>>>

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
If we gave our agent the full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates, along with a multiplexer.
\system observes the input/output truth table of the circuits.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{multiplexer}, top).

@@

  \\\midrule\multicolumn{6}{c}{\emph{String Editing}}\\\midrule
  \% solved&99\% &82\% \\
  Solve time&  0.9s&2.2s
  \\\bottomrule
  \end{tabular}
\caption{\% solved: fraction solved with 5 sec timeout. Solve time: averaged over solved tasks. MDL: $-\expect\left[\probability[x|p] \right]$. For domains other than symbolic regression MDL is 0 nats. For symbolic regression MDL is a proxy for \# of continuous degrees of freedom.}\label{baselineComparisons}  \end{table}
\pagebreak
 \section{Related Work}
 Our work is far from the first to learn to learn programs,
 an  idea that goes back to Solomonoff~\cite{solomonoff1989system}:
